RJObject Paper

### 2014-06-15 Documents/Paper/ms.tex
More writing about sinusoid data
Talking about the proposals

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}
\usepackage{parskip}

@@

\section{Sinusoidal Example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different periods, amplitudes,
and phases. The signal is observed at various times $\{t_i\}_{i=1}^N$ with
noise, and we want to use the resulting data to infer the number of sinusoids
$N$, along with the periods $\{T_i\}_{i=1}^N$, amplitudes $\{A_i\}_{i=1}^N$,
and phases $\{\phi_i\}_{i=1}^N$.
This kind of model has many applications\citep[see e.g.][]{bretthorst}.

@@

@@

%\section{``Transit'' Example}

\section*{Acknowledgements}
This work is supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand. I would like to thank the following
people for valuable conversations and inspiration:
Anna Pancoast (UCSB), David Hogg (NYU), Daniel Foreman-Mackey (NYU),
Courtney Donovan (Auckland), Tom Loredo (),
John Skilling (MaxEnt Data Consultants), and Daniela Huppenkothen ().

>>>>

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}

@@

\section{Metropolis proposals for the general problem}
We will now define a set of proposal distributions that could be used to
sample the prior distribution
$p(N, \alpha, \{x_i\}) = p(N) p(\alpha) \prod_{i=1}^N p(\{x_i\} | \alpha)$.
These proposals will need to satisfy detailed balance in order to be valid
when used inside DNS.

\section{Sinusoidal example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different periods, amplitudes,
and phases. The signal is observed at various times $\{t_i\}_{i=1}^N$ with
noise, and we want to use the resulting data to infer the number of sinusoids
$N$, along with the periods $\{T_i\}_{i=1}^N$, amplitudes $\{A_i\}_{i=1}^N$,
and phases $\{\phi_i\}_{i=1}^N$.
This kind of model has many applications\citep[see e.g.][]{bretthorst}.

@@

The true values of the parameters are $N=2$, $\mathbf{A} = \{1, 0.3\}$,
$\mathbf{T}=\{30, 2\}$, and $\boldsymbol{\phi} = \{0, 1\}$. The signal was
observed at $n=1001$ points equally spaced between $t=0$ and $t=100$. The data
is displayed in Figure~\ref{fig:sinewave_data}.

@@

%\section{``Transit'' example}

\section*{Acknowledgements}
This work is supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand. I would like to thank the following
people for valuable conversations and inspiration:
Anna Pancoast (UCSB), David Hogg (NYU), Daniel Foreman-Mackey (NYU),
Courtney Donovan (Auckland), Tom Loredo (), Iain Murray (Edinburgh),
John Skilling (MaxEnt Data Consultants), and Daniela Huppenkothen ().
